---
title: "Amenities Cleaning"
output: html_document
---
```{r}
library(sf)
library(dplyr)
library(tidyverse)
library(xml2)
library(rvest)
library(curl)
library(ggmap)
library(magrittr)
library(XML)
library(curl)
library(stringr)
library(jsonlite)
```


##1. MRT Data

The MRT data was taken from Data.Gov.Sg and also Kaggle. These files were then merged to get the address, station name, station and coordinates of the MRT stations. 

```{r station urls}
all_stations <- read.csv("train-station-chinese-names.csv")

#remove ten mile junction station and teck lee (closed)
station_data <- all_stations[which(! all_stations$stn_code %in% c('BP14','PW2')),]
rownames(station_data) <- NULL

station_name_url <- paste0(str_replace_all(station_data$mrt_station_english,' ','-'),'-station')
all_station_url <- paste0('https://landtransportguru.net/',station_name_url)
```

### Create Function to scrap address
```{r station_info}
station_info <- function(station_url){
  page <- read_html(station_url)
  #closeAllConnections()
  
  con <- html_nodes(page,"#summarybox tr:nth-child(3) td+ td")
  con2 <- html_nodes(page,".entry-content div tr:nth-child(3) td+ td")
  con <- html_text(con)
  con2 <- html_text(con2)
  address <- ifelse(length(con)==0,con2,con)
  address <- str_remove_all(address,'\n')
  address <- str_remove_all(address,'\\s\\(.*')
  
  return (address)
  #df1 <- data.frame(address)
  #return (df1)
}
```

### Get MRT/LRT address 

```{r get all mrt addresses}
station_data2 <- station_data
x=1
for (i in all_station_url) {
  station_data2$address[x] <- station_info(i)
  x = x+1
  Sys.sleep(0.1)
}

#save to csv file
write.csv(station_data2,"station_address.csv", row.names = TRUE)
```

### Lat and lon coordinates were added and we checked for errors 

```{r match lat and lon to mrt}
lat_lon <- read.csv("mrt_lrt_data.csv")
station_data_merge <- merge(x=station_data2,y=lat_lon,by.x="mrt_station_english",by.y = "station_name",all.x = TRUE)

#check for lat/lon error
con <- station_data_merge$lat[duplicated(station_data_merge$lat)]
dat <- station_data_merge[which(station_data_merge$lat %in% con),]
dat[order(dat$lat),]

#Admiralty address is wrong, change to correct lat and lon
station_data_merge$lat[1] <- 1.440619
station_data_merge$lng[1] <- 103.800967

head(station_data_merge)
write.csv(station_data_merge,"station_data.csv", row.names = TRUE)
```


## 2. Malls

The malls data was scrapped from www.malls.com to get all the shopping malls in Singapore listed in that website. Using geocode, we then get the malls latitude and longitude based on the addresses. 

```{r get links}
url <- "https://www.malls.com/malls/?countries=377&space=&m_type=1"
page <- read_html(url)
#closeAllConnections()

alpha_linktext <- html_nodes(page,".abc a") 
base <- "https://www.malls.com"
all_details_url <- paste0(base,html_attr(alpha_linktext,"href"))

get_mall_detail <- function(url){
  page <- read_html(url)
  #closeAllConnections()
  
  malls <- html_nodes(page, ".text-block a")
  malls <- html_text(malls)
  
  address <- html_nodes(page, "#content-wrapper li:nth-child(1)")
  address <- html_text(address)
  address <- str_remove(address,"ADDRESS: ")
  
  df1 <- data.frame(malls, address)
  return (df1)
}
```

### Get mall details
```{r get malls details}
malls_df <- data.frame()
for (i in all_details_url){
  malls_df <- rbind(malls_df,get_mall_detail(i))
  Sys.sleep(0.1)
}

malls_df$malls[79] <- "313@Somerset"
malls_df$malls[70] <- "Velocity@Novena Square"
malls_df$malls[45] <- "Paragon"

malls_df$address[8] <- "1 Woodlands Square, Singapore 738099"
malls_df$address[9] <- "2 Tampines Central 5, #01-32 Century Square, Singapore 529509"
malls_df$address[12] <- "180 Kitchener Rd, Singapore 208539"
malls_df$address[13] <- "1 Raffles Link, Singapore 039393"
malls_df$address[30] <- "1 Jurong West Central 2, Singapore 648886"
malls_df$address[34] <- "2 Bayfront Ave Marina Bay Sands, Singapore 018972"
malls_df$address[35] <- "6 Raffles Boulevard, Singapore 039594"
malls_df$address[36] <- "9 Raffles Boulevard, Singapore 039596"
malls_df$address[37] <- "45 Syed Alwi Road, Singapore 207704"
malls_df$address[40] <- "930 Yishun Ave 2, Singapore 769098"
malls_df$address[42] <- "181 Orchard Road, Singapore 238896"
malls_df$address[43] <- "277 Orchard Rd, Singapore 238858"

malls_df$address[44] <- "390 Orchard Road, Singapore 238871"
malls_df$address[48] <- "1 Selegie Rd, Singapore 188306"
malls_df$address[55] <- "30 Sembawang Dr, Singapore 757713"
malls_df$address[56] <- "3 Temasek Blvd, Singapore 038983"
malls_df$address[57] <- "10 Tampines Central 1, Singapore 529536" 
malls_df$address[58] <- "4 Tampines Central 5, Singapore 529510"
malls_df$address[67] <- "111 Somerset Rd, Singapore 238164"
malls_df$address[69] <- "491 River Valley Road, Singapore 248371"
malls_df$address[70] <- "238 Thomson Road, Singapore 307683"

malls_df$address[59] <- "163 Tanglin Road, Singapore 247933"
malls_df$address[60] <- "6 Eu Tong Sen Street, Singapore 059817"
malls_df$address[63] <- "33 Sengkang West Avenue, Singapore 797653"
malls_df$address[38] <- "23 Serangoon Central, Singapore 556083"

malls_df$address[72] <- "83 Punggol Central, Singapore 828761"
malls_df$address[73] <- "154 West Coast Rd, Singapore 127371"
malls_df$address[76] <- "1 Pasir Ris Central Street 3, Singapore 518457"
malls_df$address[78] <- "112 East Coast Rd (Joo Chiat Rd), Singapore 428802"

write.csv(malls_df,"malls_data1.csv", row.names = TRUE)
```

### Get latitude and Longtitude for malls
```{r get lat/lon for malls}
malls_df2 <- read.csv("malls_data1.csv")

for (i in 1:length(malls_df2$address)){
  result <- geocode(malls_df2$address[i], output = "latlona", source="google")
  malls_df2$lat[i] <- as.numeric(result[2])
  malls_df2$lon[i] <- as.numeric(result[1])
}

#get lat and lon for century square
malls_df2$lat[9] <- 1.352403
malls_df2$lon[9] <- 103.943857

head(malls_df2)

write.csv(malls_df2,"malls_data2.csv", row.names = TRUE)
```


## 3. Nature parks

The raw data of the names and location of the nature parks are gotten from https://data.gov.sg/dataset/parks, as a kml file. Then, we converted the kml file into a dataframe and extracted the necessary data. Some data cleaning was done as the original data had unclean formats when converted into a dataframe.

```{r}
parks <- st_read("parks-kml.kml")
parks_coord <- parks$geometry
parks_desc <- parks$Description
parks_desc <- data.frame(parks_desc)
parks_coord <- data.frame(parks_coord)

extract_name <- function(chunk) {
  name <- gsub(".*<th>NAME", "", chunk)
  name <- gsub("</td>.*", "", name)
  name <- gsub(".*<td>", "", name)
  return(name)
}

parks_df <- data.frame(sapply(parks_desc, extract_name))
parks_df <- cbind(parks_df, parks_coord)
names(parks_df) <- c("name", "coord")
parks_df <- separate(parks_df, 2, c("longitude", "latitude", "zero"), sep=",")
parks_df <- parks_df[-4] #remove column with zeros
parks_df$latitude <- substr(parks_df$latitude, 3, nchar(parks_df$latitude)) #get the latitude/longitude columns cleaned

write.csv(parks_df, "Parks.csv", row.names=TRUE)
```


## 4. Clinics

As there are many CHAS clinics around Singapore and since these clinics can be easily accessed, it is highly likely that most Singaporeans would visit these clinics when they fall sick. The CHAS clinics kml was taken from Data.gov.sg [https://data.gov.sg/dataset/chas-clinics] and we scraped data from the kml file. There was no data cleaning done for this file as all information was already presented accurately.
```{r}
link <- "chas-clinics-kml.kml"

chas.clinics <- st_read(link)
clinics_desc <- chas.clinics$Description

extract_name <- function(chunk) {
  name <- gsub(".*<th>HCI_NAME", "", chunk)
  name <- gsub("</td>.*", "", name)
  name <- gsub(".*<td>", "", name)
  return(name)
}

clinics_df <- data.frame(sapply(clinics_desc, extract_name))
chas.coord <- st_coordinates(chas.clinics) %>% as.data.frame()
chas.coord <- chas.coord[,-3]

chas.coord <- cbind(chas.coord, clinics_df)

chas.coord <- chas.coord %>% rename(lon=X, lat=Y, name= sapply.clinics_desc..extract_name.)

write.csv(chas.coord,"chas.csv")
```

## 5. Schools

Next, we scrapped data for schools, using the function geocode. However as some of the latitude and longitude data scraped from Google maps is wrong, we had to do some data cleaning and changed those data manually.

```{r}
Schools <- read.csv("general-information-of-schools.csv")
Schools_lat_lon <- geocode(Schools$address)
head(Schools_lat_lon)
Schools <- cbind(Schools_lat_lon, Schools$school_name)
head(Schools)
```


```{r}
Schools$lon[151] <- 103.7648
Schools$lat[151] <- 1.301510

Schools$lon[287] <- 103.7581
Schools$lat[287] <- 1.3097

Schools$lon[50] <- 103.8742
Schools$lat[50] <- 1.3343

Schools$lon[247] <- 103.7743
Schools$lat[247] <- 1.3137

Schools$lon[126] <- 103.7839
Schools$lat[126] <- 1.317730

Schools$lon[231] <- 103.8078
Schools$lat[231] <- 1.295890

Schools$lon[70] <- 103.8913
Schools$lat[70] <- 1.305490

Schools$lon[188] <- 103.7733
Schools$lat[188] <- 1.310100

Schools$lon[275] <- 103.8286
Schools$lat[275] <- 1.3229

Schools$lon[113] <- 103.49258
Schools$lat[113] <- 1.17218

Schools$lon[18] <- 103.8348
Schools$lat[18] <- 1.3179

Schools$lon[15] <- 103.8348
Schools$lat[15] <- 1.3185

Schools$lon[181] <- 103.8024
Schools$lat[181] <- 1.3305

Schools$lon[100] <- 103.476785
Schools$lat[100] <- 1.180511

Schools$lon[276] <- 103.4938
Schools$lat[276] <- 1.1925

Schools$lon[260] <- 103.7891
Schools$lat[260] <- 1.4267

Schools$lon[163] <- 103.8783
Schools$lat[163] <- 1.3417

Schools$lon[59] <- 103.7676
Schools$lat[59] <- 1.36676

Schools$lon[51] <- 103.8754
Schools$lat[51] <- 1.335870

Schools$lon[290] <- 103.8976
Schools$lat[290] <- 1.308566

Schools$lon[99] <- 103.476785
Schools$lat[99] <- 1.180511

Schools$lon[16] <- 103.7807
Schools$lat[16] <- 1.30287

Schools$lon[235] <- 103.8062
Schools$lat[235] <- 1.33031

Schools$lon[306] <- 103.8220
Schools$lat[306] <- 1.4526

Schools$lon[232] <- 103.8132
Schools$lat[232] <- 1.29401

Schools$lon[183] <- 103.8077
Schools$lat[183] <- 1.3213

Schools$lon[56] <- 103.9173
Schools$lat[56] <- 1.30686

Schools$lon[204] <- 103.8371
Schools$lat[204] <- 1.2867

Schools$lon[281] <- 103.8572
Schools$lat[281] <- 1.30412

write.csv(Schools,"schools.csv")
```


## 6. HDB Data 

As the data from https://data.gov.sg/dataset/price-range-of-hdb-flats-offered only has up to year 2018, we used data from https://www.hdb.gov.sg/cs/infoweb/residential/buying-a-flat/new/sales-launches/bto-sbf-open-booking as well
```{r}

URL <- 'https://data.gov.sg/api/action/datastore_search?resource_id=d23b9636-5812-4b33-951e-b209de710dd5&limit=1000'
data <- fromJSON(URL)

data <- data[[3]] 
head(data)
```

